\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-09-09 Latex/paper.tex
# convexity sofr example (not end)

\begin{align*}
\eta_s &= \sigma \exp(-ks)\\
\beta(s,u, x_0, \hat{y}_s) &= \sigma \exp(-ku) \\
\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}
\end{align*}
 Therefore, from the last equalities and (\ref{convexity_ois_future}), we have that
\begin{equation}
 \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \frac{\sigma^{2}}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \exp(-ku)   \frac{\exp(-ks) - \exp(-kt_1)}{k} du ds
\end{equation}
\end{example}
Now, in order to compute the convexity adjustmen for the average case, we  wil use (\ref{log_approximation}) with 
\begin{align*}
x &= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right)\\
\epsilon &=  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
\end{align*} 
we can calculate the adjusment for $R_{avg}(t_0,t1)$
\begin{align*}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) &\approx \frac{\log\left(1+(t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)\right)}{t_1 - t_0} \\
&-\frac{1}{2(1 + (t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right))^{2}} \int_{0}^{t_1}\left(\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  du\right)^{2} ds
\end{align*}

>>>>

\begin{align*}
\eta_s &= \sigma \exp(-ks)\\
\beta(s,u, x_0, \hat{y}_s) &= \sigma \exp(-ku) \\
\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}
\end{align*}
 Therefore, from the last equalities and (\ref{convexity_ois_future}), we have that
\begin{align*}
 \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) &\approx F(0,t_0,t_1) + \frac{\sigma^{2}}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \exp(-ku)   \frac{\exp(-ks) - \exp(-kt_1)}{k} du ds \\
 &\approx  F(0,t_0,t_1) + \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{0}^{t_1} (\exp(-ks) - \exp(-kt_1))(\exp(-k\max(s,t_0)) - \exp(-kt_1))) ds \\
 &\approx  F(0,t_0,t_1) + \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{0}^{t_0} (\exp(-ks) - \exp(-kt_1))(\exp(-kt_0) - \exp(-kt_1))) ds  \\
 &+ \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{t_0}^{t_1} (\exp(-ks) - \exp(-kt_1))^{2} ds
\end{align*}
It is easy to show with a little bit of algebra that
(tengo que terminarlo)
\end{example}
Now, in order to compute the convexity adjustmen for the average case, we  wil use (\ref{log_approximation}) with 
\begin{align*}
x &= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right)\\
\epsilon &=  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
\end{align*} 
we can calculate the adjusment for $R_{avg}(t_0,t1)$
\begin{align*}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) &\approx \frac{\log\left(1+(t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)\right)}{t_1 - t_0} \\
&-\frac{1}{2(1 + (t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right))^{2}} \int_{0}^{t_1}\left(\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  du\right)^{2} ds
\end{align*}
